Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-12 docs/ms.tex
Update ms.tex

One thing to note is that the conditional probability of g in one patch only explicitly depends on $\alpha$, but not g in other patches. Therefore
with $\alpha$ fixed, the posterior distributions of reduced shear in different patches are independent from each other. 
\begin{equation}
p(\vec{g}_{1}....\vec{g}_{n}|\alpha,Data)=p(\vec{g}_{1}|\alpha,Data_{1})....p(\vec{g}_{n}|\alpha,Data_{n})
\end{equation}
Therefore sampling reduced shear g from conditional distribution can be reduced to 2D sampling problem, which can be done very quickly.

@@

Finally we can put on some noise on $\epsilon_{\ell}$ to get the
observed ellipticity $\epsilon_{ob}$. For simplicity we've only considered
the situation when P($\epsilon_{ob}|\epsilon_{\ell})$ is a 2D Gaussian.

>>>>

One thing to note is that the conditional probability of g in one patch only explicitly depends on $\alpha$, but not g in other patches. Therefore
With $\alpha$ fixed, the posterior distributions of reduced shear in different patches are independent from each other. 
\begin{equation}
p(\vec{g}_{1}....\vec{g}_{n}|\alpha,Data)=p(\vec{g}_{1}|\alpha,Data_{1})....p(\vec{g}_{n}|\alpha,Data_{n})
\end{equation}
Therefore sampling reduced shear g from the conditional probability distribution can be reduced to a 2D sampling problem, which can be done very quickly.

@@

Finally we can add noise on $\epsilon_{\ell}$ to get the
observed ellipticity $\epsilon_{ob}$. For simplicity we've only considered
the situation when P($\epsilon_{ob}|\epsilon_{\ell})$ is a 2D Gaussian.
